Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-05-02 article.tex
Fix typo

\begin{figure}
  \centering
  \includegraphics[width = \textwidth]{workflow3.png}
  \caption{
    \texttt{pirouette} pipeline.
    The pipeline starts from a phylogeny (1a) simulated by the generative tree prior 
    $\mathit{p_{G}}$.
    The phylogeny is converted to an alignment (2a) using the generative alignment model 
    $\mathit{A} = (\mathit{c_{G}}, \mathit{s_{G}})$, composed by a clock and a site models. 
    The user supplies one or more experiments.
    For each candidate experiment $\mathit{X_{i}}$ 
    (a tuple of inference model $\mathit{I_{i}}$ and condition $\mathit{C_{i}}$),
    if its condition $\mathit{C_{i}}$ is 
    satisfied (which can depend on the alignment), 
    the corresponding inference model $\mathit{I} = \mathit{I_{i}}$ is selected 
    to be used in the next step.
    The inference models (3) of the selected experiments use the alignment (2a) 
    to each create a Bayesian posterior of (parameter estimates and) 
    phylogenies (4a). 
    Each of the posteriors' trees is compared to the true phylogeny (1a) 
    using error measure $\mathit{E}$, 
    resulting in an error distribution (5a). 
    Optionally, for each selected inference model a twin pipeline can be run.
    A twin phylogeny (1b) can be generated from the original 
    phylogeny (1a) using the tree prior $\mathit{p_{I}}$ of the selected inference model (3).
    Analogously, a twin alignment is simulated from the twin phylogeny along with clock model $\mathit{c_{I}}$ and site model $\mathit{s_{I}}$ imported from the selected inference model.
    The twin pipeline mimics the procedure of the main pipeline, resulting in a twin error distribution (5b).
  }
  \label{fig:pipeline}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width = \textwidth]{workflow3.png}
  \caption{
    \texttt{pirouette} pipeline.
    The pipeline starts from a phylogeny (1a) simulated by the generative tree prior 
    $\mathit{p_{G}}$.
    The phylogeny is converted to an alignment (2a) using the generative alignment model 
    $\mathit{A} = (\mathit{c_{G}}, \mathit{s_{G}})$, composed by a clock and a site model. 
    The user supplies one or more experiments.
    For each candidate experiment $\mathit{X_{i}}$ 
    (a tuple of inference model $\mathit{I_{i}}$ and condition $\mathit{C_{i}}$),
    if its condition $\mathit{C_{i}}$ is 
    satisfied (which can depend on the alignment), 
    the corresponding inference model $\mathit{I} = \mathit{I_{i}}$ is selected 
    to be used in the next step.
    The inference models (3) of the selected experiments use the alignment (2a) 
    to each create a Bayesian posterior of (parameter estimates and) 
    phylogenies (4a). 
    Each of the posteriors' trees is compared to the true phylogeny (1a) 
    using error measure $\mathit{E}$, 
    resulting in an error distribution (5a). 
    Optionally, for each selected inference model a twin pipeline can be run.
    A twin phylogeny (1b) can be generated from the original 
    phylogeny (1a) using the tree prior $\mathit{p_{I}}$ of the selected inference model (3).
    Analogously, a twin alignment is simulated from the twin phylogeny along with clock model $\mathit{c_{I}}$ and site model $\mathit{s_{I}}$ imported from the selected inference model.
    The twin pipeline mimics the procedure of the main pipeline, resulting in a twin error distribution (5b).
  }
  \label{fig:pipeline}
\end{figure}
